---
title: "Piglet 2334"
output: word_document
output: html_document
---
## Piglet physiological analysis

This document contains a summary of the animals physiological parameters whilst under anaesthesia. The data was acquired using the Marquette data acquisition system from X. Data was sampled at 12 samples per minute for the parameters of:

Umbilical artery pressure
Heart rate
End-Tidal CO2
Oxygen saturation

This document is intended to provide information about the stability of the piglet throughout the experiment.


Experimental details:

Piglet number: 2334
Sex: Male
HI commenced at :12:00
HI ended at:12:30
Infusion commenced:
Cell Dose : None (vehicle)
HTH commenced at: 14:30 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##Load appropriate packages, set working directory and load datafile ----
library(ggplot2)
library(lubridate)
library(readr)

# Set working directory
setwd("C:/Users/ellio/Downloads/html5up-hyperspace/Directory")

data <- read_csv("2334RP_r.csv")

```


```{r, include=FALSE}
# Change time format
colnames(data)[2] <- "Hours"
data <- data[-c(1:500),]
x <- data[500,2] 

# zero time 
data$Hours <- data$Hours - x


HI_HTH <- data[c(360:1080),]
colnames(HI_HTH)[2] <- "Minutes"
HI_HTH[2] <- HI_HTH$Minutes * 1/60

rec <- HI_HTH[c(360:1080),]
HI <- HI_HTH[c(1:360),]

data$Hours <- data$Hours * 1/3600 

# Remove the other variables ----
keeps <- c("Time of Day", "Hours","ECG_hr", "BP1_mean", "BP1_syst", "BP1_dias", "Temp_1", "CO2_et", "SPO2_sat")
data <- data[keeps] 

# Remove every nth row to smooth the data
tokeep <- seq(1, nrow(data), 200)
data <- data[tokeep, ]

HI_HTH <- HI_HTH[tokeep, ]


## Create a filter mechanisms to remove artefacts ----
#Filter ----
HI$BP1_mean[HI$BP1_mean <= 5 | HI$BP1_mean >= 80 | HI$BP1_mean == HI$BP1_dias |HI$BP1_mean == HI$BP1_syst ] <- NA
HI$BP1_syst[HI$BP1_syst <= 20 | HI$BP1_syst >= 150] <- NA
HI$BP1_dias[HI$BP1_dias <= 5 | HI$BP1_dias >= 80 | HI$BP1_dias >= HI$BP1_syst] <- NA
HI$ECG_hr[HI$ECG_hr <= 50 | HI$ECG_hr >= 300] <- NA
HI$SPO2_sat[HI$SPO2_sat <= 0 | HI$SPO2_sat >= 100] <- NA
HI$CO2_et[HI$CO2_et <= 5 | HI$CO2_et >= 80] <- NA
HI <- na.omit(HI)

rec$BP1_mean[rec$BP1_mean <= 5 | rec$BP1_mean >= 80 | rec$BP1_mean == rec$BP1_dias |rec$BP1_mean == rec$BP1_syst ] <- NA
rec$BP1_syst[rec$BP1_syst <= 20 | rec$BP1_syst >= 150] <- NA
rec$BP1_dias[rec$BP1_dias <= 5 | rec$BP1_dias >= 80 | rec$BP1_dias >= rec$BP1_syst] <- NA
rec$ECG_hr[rec$ECG_hr <= 50 | rec$ECG_hr >= 300] <- NA
rec$SPO2_sat[rec$SPO2_sat <= 0 | rec$SPO2_sat >= 100] <- NA
rec$CO2_et[rec$CO2_et <= 5 | rec$CO2_et >= 80] <- NA
rec <- na.omit(rec)

data$BP1_mean[data$BP1_mean <= 5 | data$BP1_mean >= 80 | data$BP1_mean == data$BP1_dias |data$BP1_mean == data$BP1_syst ] <- NA
data$BP1_syst[data$BP1_syst <= 20 | data$BP1_syst >= 150] <- NA
data$BP1_dias[data$BP1_dias <= 5 | data$BP1_dias >= 80 | data$BP1_dias >= data$BP1_syst] <- NA
data$ECG_hr[data$ECG_hr <= 50 | data$ECG_hr >= 300] <- NA
data$SPO2_sat[data$SPO2_sat <= 0 | data$SPO2_sat >= 100] <- NA
data$CO2_et[data$CO2_et <= 5 | data$CO2_et >= 80] <- NA
data <- na.omit(data)

```

```{r}
#Aquire summary of the cardiovascular statistics 


# Period of HI
summary(HI$ECG_hr)
summary(HI$BP1_mean)
summary(HI$BP1_syst)
summary(HI$BP1_dias)

## Period of recovery 
summary(rec$ECG_hr)
summary(rec$BP1_mean)
summary(rec$BP1_syst)
summary(rec$BP1_dias)

# Period of HTH
summary(data$ECG_hr)
summary(data$BP1_mean)
summary(data$BP1_syst)
summary(data$BP1_dias)


```


```{r}

data <- unlist(data)

## Filtered HR 
ggplot(data, aes(x = Hours, y = ECG_hr)) + 
  geom_line() +
  labs(title = "Piglet 2334: Heart rate over time",
       caption = "Experiment started on the 30/10/2018",
       y = "Heart rate (bpm)")


## Filtered HR 
ggplot(data, aes(x = Hours, y = ECG_hr)) + 
  geom_line() +
  labs(title = "Piglet 2334: Heart rate over time",
       caption = "Experiment started on the 30/10/2018",
       y = "Heart rate (bpm)")

## Filtered Sats
ggplot(data, aes(x = Hours, y = SPO2_sat)) + 
  geom_line() +
  labs(title = "Piglet 2334: Oxygen saturation over time",
       caption = "Experiment started on the 30/10/2018",
       y = "O2 ssaturation")

## Filtered CO2 
ggplot(data, aes(x = Hours, y = CO2_et)) + 
  geom_line() +
  labs(title = "Piglet 2334: End-tidal carbon dioxide over time",
       caption = "Experiment started on the 30/10/2018",
       y = "End-Tidal CO2 (mmHg)")

```

```{r}
## Filtered BP 
ggplot(data, aes(Hours)) + 
  geom_rect(aes(ymin = 0, ymax = 100, xmin = 2.000, xmax = 26.000),  alpha = 0.2,fill = "blue") + #Period of hypothermia
  geom_rect(aes(ymin = 0, ymax = 100, xmin = 26.000, xmax = 36.000)) + #Period of rewarming 
  geom_rect(aes(ymin = 0, ymax = 100, xmin = -0.5, xmax = 0), fill = 'orange') + # Period of HI
  geom_ribbon(aes (ymin = BP1_dias, ymax = BP1_syst))+
  geom_line(aes (y = BP1_mean, colour="#FF9999")) +
  
  #geom_tile(aes(fill = rescale),----
# High potential to make a heat map that mirros the temperature in the backdround or as a rug along the bottom

#+     colour = "white") + scale_fill_gradient(low = "white",
#+     high = "steelblue"))

  labs(title = "Piglet 2334: Blood pressure over time",
       caption = "Experiment started on the 30/10/2018",
       y = "Blood Pressure (mmHg)")

  

```
```{r}
## Filtered BP 
ggplot(HI_HTH, aes(Minutes)) + 
  geom_rect(aes(ymin = 0, ymax = 100, xmin = 30, xmax = 60), fill = 'orange', alpha = 0.6) + # Period of HI
  geom_ribbon(aes (ymin = BP1_dias, ymax = BP1_syst))+
  geom_line(aes (y = BP1_mean, colour="#FF9999")) +
  geom_line(aes(y = 30 , colour="black", linetype = "2"))+
  

  labs(title = "Piglet 2334: Blood pressure over time",
       caption = "Experiment started on the 30/10/2018",
       y = "Blood Pressure (mmHg)")

  
  #geom_tile(aes(fill = rescale),----
# High potential to make a heat map that mirros the temperature in the backdround or as a rug along the bottom

#+     colour = "white") + scale_fill_gradient(low = "white",
#+     high = "steelblue"))

```
